A new method to estimate dark matter halo concentrations

### 2015-08-20 paper/article.tex
small corrections
added plots about the impact of the input concentration

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{percentual_diff.pdf}
\end{center}
\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with a different number of particles, $N$.
    \label{fig:results_mocks}}
\end{figure}

@@

{\bf Hace falta hacer una figura para este caso.}

@@

The method based on the maximum of the circular velocity shows a similar
behaviour $\avg{|D|}\propto N^{-1/2}$. Its accuracy is $2-5$ times less
than in our method, on the order of $20\%$ for $20$ particle halos and
$0.5\%$ for $20000$ particle halos. The method based on the direct density
fit shows the an intermediate accuracy between the other two methods.

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{mock_percentual_diff.pdf}
\end{center}
\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with a different number of particles, $N$.
    \label{fig:results_mocks}}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{mock_percentual_diff_conc_20.pdf}
\end{center}
\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with an input concentration in a different range for
  a number of particles $N=20$.
    \label{fig:results_mocks_conc_20}}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{mock_percentual_diff_conc_20000.pdf}
\end{center}
\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with an input concentration in a different range for
  a number of particles $N=20000$.
    \label{fig:results_mocks_conc_20000}}
\end{figure}

{\bf Hace falta discutir las figuras.}

@@

The method based on the maximum of the circular velocity shows a similar
behaviour $\avg{|D|}\propto N^{-1/2}$. Its accuracy is $2-5$ times less
than in our method, on the order of $20\%$ for $20$ particle halos and
$0.5\%$ for $20000$ particle halos. The method based on the direct density
fit shows the lowest accuracy for a low particle number and an intermediate
accuracy between the other two methods for a high particle number.
